Joint Power Allocation and Network Slicing in an End-to-End O-RAN System

### 2019-10-28 Latex/tex/pr.tex
last version for figures

\title{Joint Power Allocation and Network Slicing In an End to End O-RAN System
}

@@

To increase enrgy efficiency and optimize the allocation of resources, Network Slicing (NS) is considered as the best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks. Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to-end network.

In this paper, we elaborate joint NS in RAN and Core of O-RAN system to investigate the power 
of each User Equipment (UE), map slices to services and also map physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RRHs and the cost of  physical resources in a downlink channel. The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems due to the fact that sub-problems are independent. 
Heuristic algorithms are proposed to each of sub-problems in order to map slices to services, optimize power consumption and map slices to physical resources to minimize the cost of total DCs simultaneously.
\end{abstract}

@@

\section{Introduction}
O-RAN, which is the integration and expansion of C-RAN and xRAN, is expected to be a key technology in 5G Network, to enhance RAN performance.  
The idea of O-RAN comes from two opinions. Firstly, according to real-time analytic used for artificial intelligence systems, the radio access networks must be evolved to be more intelligent and flexible than before. Also O-RAN uses deep learning techniques to develop smarter layers in its architecture.
 Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces.
In an innovative O-RAN system, the programmable RAN software is decoupled from hardware, which can be run on any specific processing platforms, in order to be more flexible for mobile network operators MNOs especially for mobile virtual network operators (MVNOs)\cite{oran1}. 
Openness is the specific feature of O-RAN. Open interface is one of the most crucial properties for O-RAN to enable MNOs and MVNOs, to define their own services.
The concept of software defined network (SDN), which is the separation of control plane (CP), from user plane (UP), is deployed in an intelligent O-RAN architecture. The seperation of CP/UP is developed  through the E1 interface. Moreover, this separation, promote RRM by defining Non-RT
and Near-RT) RAN Intelligent Controller (RIC) with the A1 and E2 interfaces.
O-RAN introduced interfaces such as open fronthaul interface that maps DU and RRU, an E2 interface, and an A1 interface between orchestration/NMS layer containing the non-real-time RIC
(RIC non-RT) function and the eNB/gNB containing the near-real-time RIC
(RIC near-RT) function \cite{oranpaper}.

The core idea of C-RAN is to split the radio remote head (RRH) from baseband unit (BBU). Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities \cite{cran1}.
To communicate between BBU-Pool and RRHs, the fronthaul fiber link interface, is assumed with limited capacity. The compression of a message passed through these links is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud,motalleb2017optimal}.

xRAN technology, released in April 2018 as the next generation of RAN, has three fundamental features. The Control plane is decoupled from User plane. Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware. Moreover, open north-bound and south-bound interfaces are introduced\cite{xran}.

\begin{figure}
  \centering
    \includegraphics[scale=0.55]{c6}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure} 
To evolve servicing in 5G, separation of elements of software and hardware of network is deployed in network functions virtualization (NFV) technology. In this technology, the functionality of networks is virtualized and divided into blocks of virtual network function (VNF).
The responsibility of wireless systems of the fifth generation covers wide range types of services. In order to provide the requirements of these services, network slicing (NS) is implemented to virtualize the shared physical network into several logical end-to-end networks. 
In the NS, a specific physical network hardware, run multiple virtual networks. Each virtual network is 
defined as a slice of network \cite{lee2018dynamic}.
Three different types of NS are introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing. In Core-RAN Slicing, each slice of RAN is mapped to slices of Core. Also, UEs classified into a group of services according to their requirements. In addition, each service is mapped to one or more Core-RAN slices based on the resource of slices.
Using cloud-computing in BBU-Pool, the performance of the system is enhanced by virtualizing resources
into virtual machines (VMs).
Each VM has a computing processor in order to be run by the Virtual Network Functions (VNFs) which processed arrival data. Also, VNFs are mapped to physical resources through NS techniques\cite{frdl,luong2018novel,luong2018novel1}.

The compression of messages passed through the fronthaul link due to the limited capacity of these links is considered in \cite{simeone2016cloud,1111}. 
In \cite{motalleb2017optimal} power allocation in C-RAN architecture, with limited fronthaul capacity in clustered network is studied.
In \cite{lee2018dynamic}, dynamic network slicing is considered in Heterogeneous CRAN (H-CRAN) to maximize the weighted sum-rate. Also, two level network slicing (upper and lower level) is done. The admission of UEs is maximized using the heuristic algorithms. In addition, the allocation of BBU capacity to UEs is considered.\newline
In \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting} minimization of cost obtained by power consumption, also cloud processing and limited power for each RRH is considered. Furthermore, the processing delay of each VM and wireless transmission delay taken account. In \cite{frdl}, the processing and transmission delay is modeled as 
a M/M/1 queue. In \cite{guo2016exploiting}, M/D/1 queue is modeled for transmission delay.

In this paper, as  depicted in figure \ref{fig:c11}, the downlink of the O-RAN system is assumed. UEs are divided to different groups according to 
their service requirements. Also RAN is decoupled to slices to provide requirements of services. Optimal power allocation and joint mapping slices to services are applied. In addition, mapping slices to physical resources is taken to account.\newline
The contribution of the paper is expressed as follow:
\begin{itemize}
\item In this paper, joint network slicing and resource allocation is considered in an end to end O-RAN system.
\item UEs are categorized into different class of services based on their service requirements. RAN which contains RRHs, PRBs, and VNFs ,in the two layer of processing, are classified into different group of slices.  
\item The problem is decomposed into two independent sub-problems. 
\item Heuristic algorithms are applied for the sub-problems to efficiently obtain the solution.
\end{itemize}

The rest of the paper is organized as follows. In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical data center resources is expressed. Also, problem statements is explained and decomposed to two
different sub-problems. 
In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results, is depicted for the sub-problems.

@@

In this section, first, we first present the system model, Then we obtain achievable rates and delays for the downlink (DL) of the O-RAN architecture. Afterward, we explained physical data center resources.

@@

Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single-antenna user equipments (UEs) that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $K_s$ Physical Resource Blocks (PRBs). All RRHs in a slice that is mapped to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}. Each RRH $r \in \{1,2,...,R \}$ is mapped to BBU pool via an optical fiber link with limited fronthaul capacity.
Suppose we have two processing layers in the BBU-Pool of O-RAN system which contain VNFs. The lower layer consist of high-PHY, MAC, and RLC, and the upper layer consist of RRC, PDCP and SDAP.

@@

Also, RRHs and PRBs can serve more than one slices. 

@@

where $p_{u(v,i)}$ represents the transmission power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service, and 
$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of a wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the  transmit beamforming vector from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}$ is the power of interfering signals. Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable that illustrates whether slice $s$ is mapped to service $v$ or not. If $a_{v,s} =1$ then, $v^{th}$ service is mapped to $s^{th}$ slice; otherwise, it is not mapped.

@@

In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which, is made from signal compression in BBU.

@@

shows the channel matrix between RRH set $\mathcal{R}_s$ to UE set

@@

%The channel vector from the RRH of  $s^{th}$ slice to the $i^{th}$ UE in the $v^{th}$ service $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ is modeled as below

@@

${\sigma_q}_{r_{(s,j)}}$ is the variance of quantization noise of $j^{th}$ RRH in $s^{th}$ slice.

@@

let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from $j^{th}$ RRH in $s^{th}$ slice.

@@

Nevertheless, the rate of users on the fronthual link between BBU-Pool and the $j^{th}$ RRH in $s^{th}$ slice is formulated as \cite{simeone2016cloud, 1111}

@@

where, $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RRHs in all slices. Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the toal rates of all UEs applied for all types of services. 

@@

Our goal is to maximize sum-rate and minimize sum-power (the total power of all RRHs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow, 

@@

\eqref{c11} and \eqref{c12} indicate that the power of each RRH do not exceed the maximum power, and the power of each UE is a positive integer value, respectively. Also \eqref{c13} shows that the rate of each UE is more than a threshold. \eqref{c14} and \eqref{c15} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.  

@@

\State Sort slices according to the weighted linear combination of number of PRBs, RRHs and VNFs in two layers and the Capacity of their resources in the descending order. 

@@

\State Obtain Parameters of Systems (power and rate of UEs, rate of fronhaul links, power of RRHs)

@@

 Maxmimun transmit Power of each RRH & 40dBm \\

@@

  Maximum fronthaul capacity  & 20bits/sec/Hz \\ 

@@

  Minimum data rate &  120 kbits/sec \\ [1ex] 

@@

In Fig. \ref{fig:f1a}, energy efficiency is depicted for two different numbers of services with the different mean number of UEs in each service (the parameters for simulation listed in table \ref{table:1a}). The optimal method is obtained by using MOSEK toolbox to obtain $\boldsymbol{A}$ and CVX toolbox to obtain $\boldsymbol{P}$ and iteratively updates $\boldsymbol{A}$, $\eta$ and $\boldsymbol{P}$. The optimal method is $0.016$ bits/J/Hz better than the proposed method for $V = 6$ and $E[U_v] = 10$, and also, $0.011$ bits/J/Hz better than the proposed method for $V = 3$ and, $E[U_v] = 10$. As it is shown, the Energy Efficiency is increased as a mean number of UEs rises.

@@

    \includegraphics[width=\linewidth]{figure11}

@@

    \includegraphics[width=\linewidth]{f111}

@@

    \includegraphics[width=\linewidth]{fig2_last}

@@

It is assumed that UEs are classified based on their service requirements. Also, there is a number of slices served the services. Each slice, is consist of PRBs, RRHs, and VNFs that run on VMs. The limited fronthaul capacity is considered for the fiber links between RRHs and BBU-pool.

>>>>

\title{Joint Power Allocation and Network Slicing in an End-to-End O-RAN System
}

@@

To increase energy efficiency and optimize the allocation of resources, Network Slicing (NS) is considered as the best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks. Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to-end network.

In this paper, we elaborate joint NS in RAN and Core of O-RAN system to investigate the power
of each User Equipment (UE), map slices to services and also map physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RUs and the cost of  physical resources in a downlink channel. The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems due to the fact that sub-problems are independent.
Heuristic algorithms are proposed to each of sub-problems in order to map slices to services, optimize power consumption and map slices to physical resources to minimize the cost of total DCs simultaneously.
\end{abstract}

@@

\section{Introduction}
O-RAN, as the integration and expansion of C-RAN and xRAN, is expected to be a key technology in 5G Networks to extensively enhance the RAN performance. The core idea of C-RAN is to split the radio remote head (RU) from baseband unit (BBU). Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities \cite{cran1}. To communicate between BBU-Pool and RUs, the fronthaul fiber link interface, is assumed \cite{frdl,simeone2016cloud,motalleb2017optimal}. On the other hand, xRAN technology has three fundamental features. The control plane is decoupled from user plane. Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware. Moreover, open north-bound and south-bound interfaces are introduced \cite{xran}.

O-RAN virtualizes the elements of the radio access networks, separate them and define appropriate open interfaces for connection of these elements. Moreover,O-RAN uses machine learning techniques to develop smarter RAN layers in its architecture. In an innovative O-RAN system, the programmable RAN software is decoupled from hardware, which can be run on any specific processing platforms \cite{oran1}.

Openness is the specific feature of O-RAN. Open interface is one of the most crucial properties for O-RAN to enable mobile network operators (MNOs) to define their own services.
The concept of software defined network (SDN), which is the separation of control plane (CP), from user plane (UP), is deployed in an intelligent O-RAN architecture. Moreover, this separation promotes RRM to use non-realtime (RT) and near-realtime (NRT) RAN Intelligent Controller (RIC). 
In the O-RAN architecture, distributed unit (DU) is a logical node hosting RLC/MAC/High-PHY layer. 
Moreover, central unit (CU) is a logical node hosting RRC, SDAP and PDCP.
Also, radio unit (RU),  is a logical node hosting LOW-PHY layer and 
RF processing \cite{oranpaper}.
O-RAN introduces interfaces such as open fronthaul interface that maps DU and RRU, an E2 interface, and an A1 interface between orchestration/NMS layer containing the non-real-time RIC
(RIC non-RT) function and the eNB/gNB containing the near-real-time RIC
(RIC near-RT) function.

\begin{figure}
  \centering
    \includegraphics[scale=0.55]{c6.pdf}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure}

To evolve servicing in 5G networks, separation of elements of software and hardware of network is employed and is referred to as network functions virtualization (NFV). Virtual network function (VNF) are functional blocks of the system in this case. 5G networks are expected to host several services with different requirements simultaneously. Network slicing is considered as a solution for such demand. A network slice is a logical end-to-end network which provide service with specific requirements. Multiple network slices run on the same physical network infrastructure which are managed and operate independently \cite{lee2018dynamic}. Slicing can be defined for the RAN, for the core or both of these networks \cite{ns1}. In core-RAN Slicing, each slice of RAN is attached to a slice of core.

Based on their type of request, UEs are classified into various services where UEs in the same service has similar service requests. In addition, each service is mapped to one or more slices based on the resource of the slices. Each VNF of the ORAN is mapped to one or some virtual machines (VMs) in the data center. For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.

%The compression of messages passed through the fronthaul link due to the limited capacity of these links is considered in \cite{simeone2016cloud,1111}.
In \cite{oranT},  the evolution of RAN in the  5G network is described. The architecture of C-RAN and X-RAN is expressed and development of the O-RAN from C-RAN and X-RAN is explained. Also requirements of the network in terms of capacity and latency is taken account.
In \cite{oran12},  the O-RAN architecture, is studied. The eight work groups include focus areas of O-RAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software is discussed.
In \cite{motalleb2017optimal}, power allocation in C-RAN architecture, with limited fronthaul capacity in clustered network is studied.
In \cite{lee2018dynamic}, dynamic network slicing is considered in Heterogeneous CRAN (H-CRAN) to maximize the weighted sum-rate. Also, two level network slicing (upper and lower level) is done. The admission of UEs is maximized using the heuristic algorithms. In addition, the allocation of BBU capacity to UEs is considered.\newline
In \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting} minimization of cost obtained by power consumption, also cloud processing and limited power for each RU is considered. Furthermore, the processing delay of each VM and wireless transmission delay taken account. In \cite{frdl}, the processing and transmission delay is modeled as a M/M/1 queue. In \cite{guo2016exploiting}, M/D/1 queue is modeled for transmission delay.

In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The RAN is divided to three layers including RU, DU, and CU with open interfaces. DU and CU are running on general purpose data centers. UEs are divided to different services according to their service requirements. RAN resources are decoupled to slices to provide requirements of services. Optimal power allocation and joint mapping of slices to services are applied. In addition, mapping slices to physical resources is taken to account. The contribution of the paper is expressed as follow:
\begin{itemize}
\item In this paper, joint network slicing and resource allocation is considered in an end to end O-RAN system.
\item UEs are categorized into different class of services based on their service requirements. RAN which contains RUs, PRBs, and VNFs ,in the two layer of processing, are classified into different group of slices.
\item The problem is decomposed into two independent sub-problems.
\item Heuristic algorithms are applied for the sub-problems to efficiently obtain the solution.
\end{itemize}

The rest of the paper is organized as follows. In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical data center resources is expressed. Then, problem statement is explained and decomposed into two independent sub-problems.
In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results are provided for the problem.

@@

In this section, first, we  present the system model. Then, we obtain achievable rates and delays for the downlink (DL) of the O-RAN system. Afterward, we discuss about assignment of physical data center resources.

@@

Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $, consists of $U_v$
single-antenna user equipments (UEs) that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ Physical Resource Blocks (PRBs). All RUs in a slice that is mapped to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}. Each RU $r \in \{1,2,...,R \}$ is mapped to DU via an optical fiber link with limited fronthaul capacity.
Suppose we have two processing layers in the DU/CU of O-RAN system which contain VNFs. The lower layer consist of high-PHY, MAC, and RLC, and the upper layer consist of RRC, PDCP and SDAP.

@@

Also, RUs and PRBs can serve more than one slices.

@@

where $p_{u(v,i)}$ represents the transmission power allocated by RUs to $i^{th}$ UE in $v^{th}$ service, and
$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of a wireless link from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the  transmit beamforming vector from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}$ is the power of interfering signals. Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable that illustrates whether slice $s$ is mapped to service $v$ or not. If $a_{v,s} =1$ then, $v^{th}$ service is mapped to $s^{th}$ slice; otherwise, it is not mapped.

@@

In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which, is made from signal compression in DU.

@@

shows the channel matrix between RU set $\mathcal{R}_s$ to UE set

@@

%The channel vector from the RU of  $s^{th}$ slice to the $i^{th}$ UE in the $v^{th}$ service $\boldsymbol{h}_{\mathcal{R}_s,u_{(v,i)}}\in \mathbb{C}^{{R}_s}$ is modeled as below

@@

${\sigma_q}_{r_{(s,j)}}$ is the variance of quantization noise of $j^{th}$ RU in $s^{th}$ slice.

@@

let $\bar{p}_{r_{(s,j)}}$ denote the power of transmitted signal from $j^{th}$ RU in $s^{th}$ slice.

@@

Nevertheless, the rate of users on the fronthual link between DU and the $j^{th}$ RU in $s^{th}$ slice is formulated as \cite{simeone2016cloud, 1111}

@@

where, $P_r^{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{s=1}^{S}\sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}$ is the total power consumption of all RUs in all slices. Also, $\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A}) = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} $ is the toal rates of all UEs applied for all types of services.

@@

Our goal is to maximize sum-rate and minimize sum-power (the total power of all RUs and the total power consumption of baseband processing at all DCs) simultaneously, with the presence of constraints which is written as follow,

@@

\eqref{c11} and \eqref{c12} indicate that the power of each RU do not exceed the maximum power, and the power of each UE is a positive integer value, respectively. Also \eqref{c13} shows that the rate of each UE is more than a threshold. \eqref{c14} and \eqref{c15} expressed the limited capacity of the fronthaul link, and the limited delay of receiving signal, respectively.

@@

\State Sort slices according to the weighted linear combination of number of PRBs, RUs and VNFs in two layers and the Capacity of their resources in the descending order.

@@

\State Obtain Parameters of Systems (power and rate of UEs, rate of fronhaul links, power of RUs)

@@

 Maxmimun transmit Power of each RU & 40dBm \\

@@

  Maximum fronthaul capacity  & 200bits/sec/Hz \\

@@

  Minimum data rate &  10 bits/sec/Hz \\ [1ex]

@@

In Fig. \ref{fig:f1a}, energy efficiency is depicted for two different numbers of services with the different mean number of UEs in each service (the parameters for simulation listed in table \ref{table:1a}). The optimal method is obtained by using MOSEK toolbox to obtain $\boldsymbol{A}$ and CVX toolbox to obtain $\boldsymbol{P}$ and iteratively updates $\boldsymbol{A}$, $\eta$ and $\boldsymbol{P}$. The optimal method is $0.1$ bits/J/Hz better than the proposed method for $V = 6$ and $E[U_v] = 10$, and also, $0.09$ bits/J/Hz better than the proposed method for $V = 3$ and, $E[U_v] = 10$. As it is shown, the Energy Efficiency is increased as a mean number of UEs rises.

@@

    \includegraphics[width=\linewidth]{fig1_last}

@@

    \includegraphics[width=\linewidth]{f112}

@@

    \includegraphics[width=\linewidth]{fig22_last}

@@

It is assumed that UEs are classified based on their service requirements. Also, there is a number of slices served the services. Each slice, is consist of PRBs, RUs, and VNFs that run on VMs. The limited fronthaul capacity is considered for the fiber links between RUs and DU
